Summary stats for paper

### 2022-01-28 analysis/SI_figs.Rmd
updated for resubmission!

ggsave(sprintf("analysis/si_figs/supp_map_fig_%s.jpg", spp_group))
}

@@

ggsave(sprintf("analysis/si_figs/supp_map_fig_%s.jpg", data_type_2_id))

@@

ggsave("analysis/si_figs/workflow_fig_1.jpg")

@@

ggsave("analysis/si_figs/workflow_fig_2.jpg")

>>>>

ggsave(sprintf("analysis/si_figs/supp_map_fig_%s.jpg", spp_group), units = "in", width = 8.07, height = 5.34)
}

@@

ggsave(sprintf("analysis/si_figs/supp_map_fig_%s.jpg", data_type_2_id), units = "in", width = 8.07, height = 5.34)

@@

ggsave("analysis/si_figs/workflow_fig_1.jpg", units = "in", width = 8.07, height = 5.34)

@@

ggsave("analysis/si_figs/workflow_fig_2.jpg", units = "in", width = 8.07, height = 5.34)

### 2022-01-28 analysis/match_data_sources.Rmd
updated for resubmission!

@@

# read in our sources spreadsheet (manually uploaded by GC)
sources <- read_csv("analysis/data/mariculture_mapping_sources.csv") %>%
  clean_names() %>%
  mutate(type = case_when(species == "Salmonids" ~ "salmon",
                          species == "Unfed or algae fed shellfish" ~ "bivalve",
                          species == "Shrimp" ~ "shrimp", 
                          species == "Tuna" ~ "tuna", 
                          species == "General Marine Fish" ~ "marine_fish_general", 
                          species == "Crustaceans" ~ "crustaceans")) %>%
mutate(species_group = case_when(species == "Salmonids" ~ "Salmonidae fish",
                          species == "Unfed or algae fed shellfish" ~ "Unfed or algae fed bivalve molluscs",
                          species == "Shrimp" ~ "Shrimps and prawns", 
                          species == "Tuna" ~ "Bluefin tuna", 
                          species == "General Marine Fish" ~ "General marine fish", 
                          species == "Crustaceans" ~ "Non-shrimp crustaceans")) %>% 
  mutate(data_year_number_of_farms = as.character(data_year_number_of_farms)) %>%
  mutate(data_type_2 = case_when(
    known_farms_location > 0 & known_farms_no_location == 0 & estimated_farms == 0 ~ "A",
    known_farms_location == 0 & known_farms_no_location > 0 & estimated_farms == 0 ~ "B",
    known_farms_location > 0 & known_farms_no_location > 0 & estimated_farms == 0 ~ "C",
    known_farms_location > 0 & known_farms_no_location == 0 & estimated_farms > 0 ~ "D",
    known_farms_location == 0 & known_farms_no_location == 0 & estimated_farms > 0 ~ "F",
  )) %>%
  mutate(data_type_2 = ifelse(str_detect(details, "Although"), "D", data_type_2)) %>%
  mutate(data_type_2 = ifelse(iso3c == "IND" & species == "Unfed or algae fed shellfish", "E", data_type_2)) ## fix some mismatches

## data types with comprehensive # of farms are A, B, and C. These all recieve their production/# of farms to get prod per farm.

@@

@@

# Salmon: CAN, USA
# Shrimp: USA 
# Bivalve: AUS, CAN, USA
# General marine fish: TWN

@@

@@

all_farms_sources_final <- all_farms_sources %>%
  filter(iso3c != "CAN"|species != "Salmonids") %>%
  filter(iso3c != "CAN"|species != "Unfed or algae fed shellfish") %>%
  filter(iso3c != "USA"|species != "Salmonids") %>%
  filter(iso3c != "USA"|species != "Unfed or algae fed shellfish"|data_type != "known locations") %>%
  filter(iso3c != "AUS"|species != "Unfed or algae fed shellfish"|data_type != "known locations") %>%
  filter(iso3c != "TWN"|species != "General Marine Fish"|data_type != "known locations") %>%
  filter(iso3c != "USA"|species != "Shrimp") %>%
  rbind(TWN_finfish_fix, USA_bivalve_fix, USA_salmon_fix, USA_shrimp_fix, CAN_bivalve_fix, CAN_salmon_fix, AUS_bivalve_fix) %>%
  mutate(data_year = as.numeric(data_year)) %>%
  dplyr::select(-species)

summary(all_farms_sources_final)
unique(all_farms_sources_final$data_year)
unique(sort(all_farms_sources$country))
unique(sort(all_farms_sources$iso3c)) ## 73 countries - perfect! 
unique(all_farms_sources_final$species_group)

@@

test <- all_farms %>%
  filter(iso3c == "CRI", str_detect(species_group, "hrimp")) %>%
    st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

>>>>

library(readxl)    
read_excel_allsheets <- function(filename, tibble = FALSE) {
    # I prefer straight data.frames
    # but if you like tidyverse tibbles (the default with read_excel)
    # then just pass tibble = TRUE
    sheets <- readxl::excel_sheets(filename)
    x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
    if(!tibble) x <- lapply(x, as.data.frame)
    names(x) <- sheets
    x
}

data <- read_excel_allsheets("analysis/data/mariculture_mapping_sources_raw.xlsx")

df <- plyr::ldply(data, as.data.frame) %>%
  mutate(`Data year: farm locations` = as.character(`Data year: farm locations`),
         `Data year: number of farms` = as.character(`Data year: number of farms`))

@@

# read in our sources spreadsheet (manually uploaded by GC)
sources <- df %>%
  clean_names() %>%
  mutate(type = case_when(species == "Salmonids" ~ "salmon",
                          species == "Unfed or algae fed shellfish" ~ "bivalve",
                          species == "Shrimp" ~ "shrimp", 
                          species == "Tuna" ~ "tuna", 
                          species == "General Marine Fish" ~ "marine_fish_general", 
                          species == "Crustaceans" ~ "crustaceans")) %>%
mutate(species_group = case_when(species == "Salmonids" ~ "Salmonidae fish",
                          species == "Unfed or algae fed shellfish" ~ "Unfed or algae fed bivalve molluscs",
                          species == "Shrimp" ~ "Shrimps and prawns", 
                          species == "Tuna" ~ "Bluefin tuna", 
                          species == "General Marine Fish" ~ "General marine fish", 
                          species == "Crustaceans" ~ "Non-shrimp crustaceans")) %>% 
  mutate(data_year_number_of_farms = as.character(data_year_number_of_farms)) %>%
 # mutate(estimated_farms = ifelse(is.na(estimated_farms), estimated_farms_2, estimated_farms)) %>%
  dplyr::select(-id) %>%
  mutate(data_type_2 = case_when(
    known_farms_location > 0 & known_farms_no_location == 0 & estimated_farms == 0 ~ "A",
    known_farms_location == 0 & known_farms_no_location > 0 & estimated_farms == 0 ~ "B",
    known_farms_location > 0 & known_farms_no_location > 0 & estimated_farms == 0 ~ "C",
    known_farms_location > 0 & known_farms_no_location == 0 & estimated_farms > 0 ~ "D",
    known_farms_location == 0 & known_farms_no_location == 0 & estimated_farms > 0 ~ "F",
  )) %>%
  mutate(data_type_2 = ifelse(str_detect(details, "Although"), "D", data_type_2)) %>%
  mutate(data_type_2 = ifelse(iso3c == "IND" & species == "Unfed or algae fed shellfish", "E", data_type_2)) ## fix some mismatches

## data types with comprehensive # of farms are A, B, and C. These all receive their production/# of farms to get prod per farm.

@@

test <- all_farms_sources %>%
  filter(iso3c == "CHN", 
         species_group == "Shrimps and prawns")

## will need to fix china bivalve and shrimp

sum(all_farms_sources$tonnes_per_farm) # 29639681
sum(all_prod$fao_tonnes_production) # 29623515

29623515 - 29639681 # off by about 16k.. probably because of rounding issues 
```

@@

# Salmon: CAN, USA
# Shrimp: USA, CHN 
# Bivalve: AUS, CAN, USA, CHN
# General marine fish: TWN

@@

## China bivalve fix
### There are 11 farms from ASC...

# read in ASC dataset for China bivalves
farms_chn <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "CHN") %>%
  mutate(data_quality = 2)

## so it looks like the first 11 rows are the ASC rows.. the geometries are not as precise 
CHN_bivalve_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "CHN", 
               species == "Unfed or algae fed shellfish", 
               data_type == "known locations") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
  mutate(row = row_number()) %>%
  mutate(data_source = ifelse(row %in% c(1:11), ds_1, ds_2)) %>%
  mutate(data_year = 2021) %>%
  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)

## do the same for China shrimp

farms_chn <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "CHN") %>%
  mutate(data_quality = 2)

## so it looks like the first 4 rows are the ASC rows.. the geometries are not as precise 
CHN_shrimp_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "CHN", 
               species == "Shrimp", 
               data_type == "known locations") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
  mutate(row = row_number()) %>%
  mutate(data_source = ifelse(row %in% c(1:4), ds_1, ds_2)) %>%
  mutate(data_year = 2021) %>%
  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)

@@

all_farms_sources_final <- all_farms_sources %>%
  filter(iso3c != "CAN"|species != "Salmonids") %>%
  filter(iso3c != "CAN"|species != "Unfed or algae fed shellfish") %>%
  filter(iso3c != "USA"|species != "Salmonids") %>%
  filter(iso3c != "USA"|species != "Unfed or algae fed shellfish"|data_type != "known locations") %>%
  filter(iso3c != "AUS"|species != "Unfed or algae fed shellfish"|data_type != "known locations") %>%
  filter(iso3c != "TWN"|species != "General Marine Fish"|data_type != "known locations") %>%
  filter(iso3c != "USA"|species != "Shrimp") %>%
  filter(iso3c != "CHN"|species != "Unfed or algae fed shellfish"|data_type != "known locations") %>%
  filter(iso3c != "CHN"|species != "Shrimp"|data_type != "known locations") %>%
  rbind(TWN_finfish_fix, USA_bivalve_fix, USA_salmon_fix, USA_shrimp_fix, CAN_bivalve_fix, CAN_salmon_fix, AUS_bivalve_fix, CHN_bivalve_fix, CHN_shrimp_fix) %>%
  mutate(data_year = as.numeric(data_year)) %>%
  dplyr::select(-species)

summary(all_farms_sources_final)
unique(all_farms_sources_final$data_year)
unique(sort(all_farms_sources$country))
unique(sort(all_farms_sources$iso3c)) ## 73 countries - perfect! 
unique(all_farms_sources_final$species_group)
sum(all_farms_sources_final$tonnes_per_farm) # 29639681

@@

test <- all_farms %>%
  filter(iso3c == "GBR", str_detect(species_group, "almo")) %>%
    st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

### 2022-01-28 analysis/paper_figs.Rmd
updated for resubmission!

test <- all_farms_sf %>%
  filter(iso3c == "ECU")
mapview(test, zcol = "data_type") ## one weird MFG from ASC.. i think these are fine. Justifiable since it is from the ASC...

@@

@@

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank(),
        text=element_text(family="Times New Roman")) +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c("Known locations \n N = 9,750", "Modeled locations, known number of farms \n N = 10,519", "Modeled locations, estimated number of farms \n N = 75,073"))

@@

# Combine all plots into one
plot_final <- insert_xaxis_grob(total_map, plot_x, position = "top")
plot_final <- insert_yaxis_grob(plot_final, plot_y, position = "right") 
ggdraw(plot_final)
ggsave("analysis/figs/map_fig_31km.jpg")

@@

# ## Norway
# nor_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
#   annotation_map_tile(type = "osm", zoomin = 0) + 
#   geom_spatial_point(size = 0.5, alpha = 0.7) + 
#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
#                     breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
#     coord_sf(crs = 4326, xlim = c(4, 10), ylim = c(58.5, 61.5), expand = FALSE) +
#   theme(legend.position = "bottom", 
#         legend.title=element_blank(), 
#         axis.title.x = element_blank(), 
#         axis.title.y = element_blank(),
#         legend.key = element_rect(fill = NA),
#         axis.text.x = element_text(angle = 60, hjust = 1),
#         text=element_text(family="Times New Roman"),
# panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
#   ggtitle("C")
# nor_zoom

## USA NE 
usa_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 1.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
    coord_sf(crs = 4326, xlim = c(-123.5, -122), ylim = c(47, 48), expand = FALSE) +
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
        axis.text.x = element_text(angle = 60, hjust = 1),
        text=element_text(family="Times New Roman"),
panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("C") # + 
 # scale_alpha_manual(values = c(0.7, 0.7, 1))

usa_zoom

@@

plot1
ggsave("analysis/figs/chl_ecu_zoom_31km.jpg")

## USA and China

plot2 <- (usa_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...

plot2
ggsave("analysis/figs/usa_chn_zoom_31km.jpg")

@@

>>>>

test <- all_farms_sf %>%
  filter(iso3c == "AUS")
mapview(test, zcol = "data_type") ## one weird MFG from ASC.. i think these are fine. Justifiable since it is from the ASC...

@@

test <- all_farms %>%
  group_by(data_type) %>%
  summarise(n_farms = n())
```

@@

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank(),
        text=element_text(family="Times New Roman")) +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c("Known locations \n N = 16,138", "Modeled locations, known number of farms \n N = 9,951", "Modeled locations, estimated number of farms \n N = 69,354"))

@@

# Combine all plots into one
plot_final <- insert_xaxis_grob(total_map, plot_x, position = "top")
plot_final <- insert_yaxis_grob(plot_final, plot_y, position = "right") 
ggdraw(plot_final)
ggsave("analysis/figs/map_fig_final.jpg", units = "in", width = 8.07, height = 5.34)

@@

## USA NW
# usa_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
#   annotation_map_tile(type = "osm", zoomin = 0) + 
#   geom_spatial_point(size = 1.5, alpha = 0.7) + 
#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
#                     breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
#   coord_sf(crs = 4326, xlim = c(-123, -122), ylim = c(47, 48), expand = FALSE) +
#  # coord_sf(crs = 4326, xlim = c(-80.5, -79.5), ylim = c(-3.2, -2.2), expand = FALSE) + 
#   #coord_sf(crs = 4326, xlim = c(-45, -25), ylim = c(70, 125), expand = FALSE) +
#  # st_crop(xmin = -20, xmax = 45, ymin = 30, ymax = 73) +
#   theme(legend.position = "bottom", 
#         legend.title=element_blank(), 
#         axis.title.x = element_blank(), 
#         axis.title.y = element_blank(),
#         legend.key = element_rect(fill = NA),
#         axis.text.x = element_text(angle = 60, hjust = 1),
#         text=element_text(family="Times New Roman"),
# panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
#   ggtitle("C") # + 
#  # scale_alpha_manual(values = c(0.7, 0.7, 1))
# 
# usa_zoom

## Australia 
aus_zoom <- ggplot(all_farms %>%
                     filter(iso3c == "AUS"), aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 1.3, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
coord_sf(crs = 4326, xlim = c(135.5, 138), ylim = c(-36, -34), expand = FALSE) + 
  #coord_sf(crs = 4326, xlim = c(135.8, 136.8), ylim = c(-35, -34.5), expand = FALSE) + 
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1),
        legend.key = element_rect(fill = NA),
        text=element_text(family="Times New Roman"),
panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("C")
aus_zoom

@@

plot1
ggsave("analysis/figs/chl_ecu_zoom.jpg", units = "in", width = 8.07, height = 5.35)

## AUS and China

plot2 <- (aus_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...

plot2
ggsave("analysis/figs/aus_chn_zoom.jpg", units = "in", width = 8.07, height = 5.35)

@@

plot1 / plot2
```

### 2022-01-28 analysis/paper_stats.Rmd
updated for resubmission!

sum(all_farms$tonnes_per_farm) # 29638328

@@

data_type_no_A <- all_farms %>%
  filter(data_type_2 != "A")
sum(data_type_no_A$tonnes_per_farm) # 26070193

26070193/29638328 # 0.8796108

@@

by_data_type
# A tibble: 3 x 4
#   data_type                                   n_obs total_obs   pct
#   <chr>                                       <int>     <int> <dbl>
# 1 known location                               9750     95341  10.2
# 2 modeled location, estimated number of farms 75073     95341  78.7
# 3 modeled location, known number of farms     10519     95341  11.0

# How many countries have spatial locations information?
known_countries <- all_farms %>%
  filter(data_type == "known location") %>%
  distinct(iso3c)

@@

chn_data_estimated <- all_farms %>%
  filter(iso3c == "CHN") 
# 58166 points
58166/95342 # 0.6099201 = 61%

chn_data_known <- all_farms %>%
  filter(iso3c == "CHN") %>%
  filter(data_type == "known location") # 15 locations

# Chile, Norway, and Ireland provided a substantial number of known locations (>1000).
top_known <- all_farms %>%
  filter(data_type == "known location") %>%
  group_by(iso3c) %>%
    summarise(n_obs = n())

@@

sum(no_info$tonnes_per_farm) # 155205.1

@@

155205.1/29623515 # 0.005239253

@@

However, 16 countries (representing 10% of fish and invertebrate mariculture production) had comprehensive farm locations across all taxa (i.e. no estimation or interpolation required, Table S3)
```{r}

@@

"Thirty-six of the countries in the table have comprehensive “number of farm” data across all types of mariculture they produce (data types A, B, or C), accounting for 12% of the global fish and invertebrate mariculture production (Albania, Belize, Bulgaria, Canada, Chile, Colombia, Croatia, Cyprus, Denmark, El Salvador, Faroe Islands, Finland, French Polynesia, Germany, Greece, Guatemala, Guernsey, Hong Kong, Ireland, Italy, Jersey, Madagascar, Malta, Netherlands, New Zealand, Norway, Peru, Portugal, Singapore, Slovenia, South Africa, Sri Lanka, Tunisia, Turkey, United Arab Emirates, United Kingdom)."

all_comp <- all_farms %>%
  group_by(iso3c) %>%
  mutate(check = all(data_type_2 %in% c("A", "B", "C"))) %>%
  filter(check == TRUE)
sort(unique(all_comp$country))

@@

# Albania', 'Belize', 'Bulgaria', 'Canada', 'Chile', 'Colombia', 'Croatia', 'Cyprus', 'Denmark', 'El Salvador ', 'Faroe Islands', 'Finland', 'French Polynesia', 'Germany', 'Greece', 'Guatemala', 'Guernsey', 'Hong Kong ', 'Ireland', 'Italy', 'Jersey', 'Madagascar', 'Malta', 'Netherlands', 'New Zealand', 'Norway', 'Peru', 'Portugal', 'Singapore', 'Slovenia', 'South Africa', 'Sri Lanka', 'Tunisia', 'Turkey', 'United Arab Emirates', 'United Kingdom

@@

3788091/31011413 # 0.1221515 ~ 10%

Using the country/species grouping combinations with presumed comprehensive farm count data (N=74, 17% of production included, data type A/B/C, see Table S3)
```{r}

@@

@@

@@

>>>>

sum(all_farms$tonnes_per_farm) # 29642964

@@

data_type_no_A <- all_farms %>%
  filter(data_type_2 != "A")
sum(data_type_no_A$tonnes_per_farm) # 26074829

26074829/29642964 # 0.8796296 # ~88% of production is data limited

@@

by_data_type
# A tibble: 3 x 4
#   data_type                                    n_obs total_obs   pct
#   <chr>                                        <int>     <int> <dbl>
# 1 known locations                              16032     95331  16.8
# 2 modeled locations, estimated number of farms 69348     95331  72.7
# 3 modeled locations, known number of farms      9951     95331  10.4

# How many countries have spatial locations information?
known_countries <- all_farms %>%
  filter(data_type == "known locations") %>%
  distinct(iso3c)

@@

chn_data_estimated <- all_farms %>%
  filter(iso3c == "CHN") 
# 58166 points
58166/95443 # 0.6094318 = ~61%

chn_data_known <- all_farms %>%
  filter(iso3c == "CHN") %>%
  filter(data_type == "known locations") # 5739 locations

# Chile, Norway, and Ireland provided a substantial number of known locations (>1000).
top_known <- all_farms %>%
  filter(data_type == "known locations") %>%
  group_by(iso3c) %>%
    summarise(n_obs = n())

@@

sum(no_info$tonnes_per_farm) # 156132.3

@@

156132.3/29623515 # 0.005270553

@@

However, 17 countries (representing 10% of fish and invertebrate mariculture production) had comprehensive farm locations across all taxa (i.e. no estimation or interpolation required, Table S3)
```{r}

@@

"Thirty-six countries have comprehensive “number of farm” data across all types of mariculture they produce (data types A, B, or C), accounting for 12% of the global fish and invertebrate mariculture production."

```{r}
all_comp <- all_farms %>%
  group_by(iso3c) %>%
  mutate(check = all(data_type_2 %in% c("A","B","C"))) %>%
  filter(check == TRUE)

@@

# 'Albania', 'Belize', 'Bulgaria', 'Canada', 'Chile', 'Colombia', 'Croatia', 'Cyprus', 'Denmark', 'El Salvador ', 'Faroe Islands', 'Finland', 'French Polynesia', 'Germany', 'Greece', 'Guatemala', 'Guernsey', 'Hong Kong ', 'Ireland', 'Italy', 'Jersey', 'Madagascar', 'Malta', 'Netherlands', 'New Zealand', 'Norway', 'Peru', 'Portugal', 'Singapore', 'Slovenia', 'South Africa', 'Sri Lanka', 'Tunisia', 'Turkey', 'United Arab Emirates', 'United Kingdom'

@@

3788091/31011413 # 0.1221515 ~ 12%
```

"Using the country/species grouping combinations with presumed comprehensive farm count data (N=74, 17% of production included, data type A/B/C, see Table S3)"
```{r}

@@

length(unique(test$country))

@@

test2 <- test %>%
  group_by(country, species_group) %>%
  summarise(n()) # 74 combos

@@

```{r}
by_data_type_spp <- all_farms %>%
  group_by(data_type, species_group) %>%
  summarise(n_obs = n()) %>%
  mutate(total_obs = sum(n_obs)) %>% 
  ungroup() %>%
  mutate(pct = n_obs/total_obs*100)

by_spp <- all_farms %>%
  group_by(species_group) %>%
  summarise(n_obs = n()) %>%
  mutate(total_obs = sum(n_obs)) %>% 
  ungroup() %>%
  mutate(pct = n_obs/total_obs*100)
```
